fdcoexist

### 2018-08-20 paper_simulations.Rmd
Varying strength of environmental filtering added and plot changes.

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    library("cowplot")
    library("tidyverse")
    library("directlabels")
})
# Functions --------------------------------------------------------------------
compute_moments = function(simulation_routine, trait_df = traits) {
    # CWM computation
    ab_rel = (simulation_routine$compo[,,150] /
                  rowSums(simulation_routine$compo[,,150]))
    cwm_df = ab_rel %*% trait_df
    # Values stored in moments_df
    moments_df = as.data.frame(cwm_df)
    colnames(moments_df) = "cwm"
    moments_df = tibble::rownames_to_column(moments_df, "patch")
    moments_df$env = seq(patches)
    # Add CWV
    cwv_df = (ab_rel %*% trait_df^2) - cwm_df^2
    cwv_df = as.data.frame(cwv_df)
    colnames(cwv_df) = "cwv"
    cwv_df = tibble::rownames_to_column(cwv_df, "patch")
    moments_df = dplyr::left_join(moments_df, cwv_df, by = "patch")

@@

n_patches  <- 25   # Number of patches
n_species  <- 100  # Number of species
n_gen      <- 150  # Length of model run (generations)
initpop    <- 50   # initial population size
n_traits   <- 3    # number of traits
k          <- 1.45 # Maximum growth rate
env_width  <- seq(10, 10, length.out = n_patches)  # Envtal filter strength

@@

# Relationship betwee, species trait values along the enviroment showing their
# local abundances for the different traits considered
fig_ind_landscape = function(simul_df, simul_label, n_bins = 22,
                             given_trans = "identity") {
    simul_df %>%
    select(-contains("cwm")) %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    ggplot(aes(patch_optim, trait_value, z = N)) +
    stat_summary_2d(geom = "raster", bins = n_bins, interpolate = TRUE) +
    facet_grid(vars(scenario), vars(trait_name),
               labeller = labeller(scenario = trait_scenar_names,
                                   trait_name = function(x) gsub("_", " ", x))) +
    scale_fill_viridis_c(trans = given_trans) +
    labs(x = "Environment",
         y = "Trait Value",
         fill = "Species Abundance",
         subtitle = simul_label) +
    theme(legend.position = "top")
}
```

@@

```{r no_compet_no_cor_abund_env}
plot_no_compet_no_cor_abund_env = fig_abund_env(no_compet_no_cor_df,
                                                no_compet_no_cor_label)

@@

```{r no_compet_no_cor_cwm_env}
plot_no_compet_no_cor_cwm_env = fig_cwm_env(no_compet_no_cor_df,
                                            no_compet_no_cor_label)
plot_no_compet_no_cor_cwm_env
```

```{r no_compet_no_cor_cwm_env_abund}
plot_no_compet_no_cor_cwm_env_abund = fig_cwm_env_abund(no_compet_no_cor_df,
                                                        no_compet_no_cor_label,
                                                        given_trans = "log10")

@@

```{r no_compet_low_cor_abund_env}
plot_no_compet_low_cor_abund_env = fig_abund_env(no_compet_low_cor_df,
                                                 no_compet_low_cor_label)

plot_no_compet_low_cor_abund_env
```

```{r no_compet_low_cor_cwm_env}
plot_no_compet_low_cor_cwm_env = fig_cwm_env(no_compet_low_cor_df,
                                             no_compet_low_cor_label)

plot_no_compet_low_cor_cwm_env
```

```{r no_compet_low_cor_cwm_env_abund}
plot_no_compet_low_cor_cwm_env_abund = fig_cwm_env_abund(no_compet_low_cor_df,
                                                         no_compet_low_cor_label,
                                                         given_trans = "log10")

plot_no_compet_low_cor_cwm_env_abund
```

@@

```{r no_compet_high_cor_abund_env}
plot_no_compet_high_cor_abund_env = fig_abund_env(no_compet_high_cor_df,
                                                  no_compet_high_cor_label)

plot_no_compet_high_cor_abund_env
```

```{r no_compet_high_cor_cwm_env}
plot_no_compet_high_cor_cwm_env = fig_cwm_env(no_compet_high_cor_df,
                                              no_compet_high_cor_label)
plot_no_compet_high_cor_cwm_env
```

```{r no_compet_high_cor_cwm_env_abund}
plot_no_compet_high_cor_cwm_env_abund = fig_cwm_env_abund(no_compet_high_cor_df,
                                                          no_compet_high_cor_label,
                                                          given_trans = "log10")

plot_no_compet_high_cor_cwm_env_abund
```

@@

```{r compet_no_cor_abund_env}
plot_compet_no_cor_abund_env = fig_abund_env(compet_no_cor_df,
                                             compet_no_cor_label)

plot_compet_no_cor_abund_env
```

```{r compet_no_cor_cwm_env}
plot_compet_no_cor_cwm_env = fig_cwm_env(compet_no_cor_df,
                                         compet_no_cor_label)

plot_compet_no_cor_cwm_env
```

```{r compet_no_cor_cwm_env_abund}
plot_compet_no_cor_cwm_env_abund = fig_cwm_env_abund(compet_no_cor_df,
                                                     compet_no_cor_label,
                                                     given_trans = "identity")
plot_compet_no_cor_cwm_env_abund
```

@@

```{r compet_low_cor_abund_env}
plot_compet_low_cor_abund_env = fig_abund_env(compet_low_cor_df,
                                              compet_low_cor_label)

plot_compet_low_cor_abund_env
```

```{r compet_low_cor_cwm_env}
plot_compet_low_cor_cwm_env = fig_cwm_env(compet_low_cor_df,
                                          compet_low_cor_label)

plot_compet_low_cor_cwm_env
```

```{r compet_low_cor_cwm_env_abund}
plot_compet_low_cor_cwm_env_abund = fig_cwm_env_abund(compet_low_cor_df,
                                                      compet_low_cor_label,
                                                      given_trans = "identity")

plot_compet_low_cor_cwm_env_abund
```

@@

```{r compet_high_cor_abund_env}
plot_compet_high_cor_abund_env = fig_abund_env(compet_high_cor_df,
                                               compet_high_cor_label)

plot_compet_high_cor_abund_env
```

```{r compet_high_cor_cwm_env}
plot_compet_high_cor_cwm_env = fig_cwm_env(compet_high_cor_df,
                                           compet_high_cor_label)

plot_compet_high_cor_cwm_env
```

```{r compet_high_cor_cwm_env_abund}
plot_compet_high_cor_cwm_env_abund = fig_cwm_env_abund(compet_high_cor_df,
                                                       compet_high_cor_label,
                                                       given_trans = "identity")

plot_compet_high_cor_cwm_env_abund
```

@@

>>>>

# Packages ---------------------------------------------------------------------
suppressPackageStartupMessages({
    suppressWarnings({
        library("cowplot")
        library("tidyverse")
        library("directlabels")
    })
})
# Functions --------------------------------------------------------------------
compute_moments = function(simulation_routine, trait_df = traits) {
    # CWM computation
    ab_rel = (simulation_routine$compo[,,150] /
                  rowSums(simulation_routine$compo[,,150]))
    cwm_df = ab_rel %*% trait_df
    # Values stored in moments_df
    moments_df = as.data.frame(cwm_df)
    colnames(moments_df) = "cwm"
    moments_df = tibble::rownames_to_column(moments_df, "patch")
    moments_df$env = seq(patches)
    # Add CWV
    cwv_df = (ab_rel %*% trait_df^2) - cwm_df^2
    cwv_df = as.data.frame(cwv_df)
    colnames(cwv_df) = "cwv"
    cwv_df = tibble::rownames_to_column(cwv_df, "patch")
    moments_df = dplyr::left_join(moments_df, cwv_df, by = "patch")

@@

n_patches  <- 25   # Number of patches
n_species  <- 100  # Number of species
n_gen      <- 150  # Length of model run (generations)
initpop    <- 50   # initial population size
n_traits   <- 3    # number of traits
k          <- 1.45 # Maximum growth rate
env_width  <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

@@

# Relationship betwee, species trait values along the enviroment showing their
# local abundances for the different traits considered
fig_ind_landscape = function(simul_df, simul_label, n_bins = 22,
                             given_trans = "identity") {

    simul_df <- simul_df %>%
        select(-contains("cwm")) %>%
        gather("trait_name", "trait_value", contains("trait"))

    simul_df_cwm <- simul_df %>%
        group_by(scenario, patch, trait_name) %>%
        summarise(cwm = weighted.mean(trait_value, N))

    simul_df2 <- left_join(simul_df, simul_df_cwm,
                           by = c("scenario", "patch", "trait_name"))

    ggplot(simul_df2,
           aes(patch_optim, trait_value, z = N)) +
        stat_summary_2d(geom = "raster", bins = n_bins, interpolate = TRUE) +
        geom_line(aes(patch_optim, cwm, color = "firebrick"), size = 1) +
        facet_grid(vars(scenario), vars(trait_name),
                   labeller = labeller(scenario = trait_scenar_names,
                                       trait_name = function(x) gsub("_", " ", x))) +
        scale_fill_viridis_c(trans = given_trans) +
        scale_color_manual(name = "CWM", values = c(firebrick = "grey80"),
                           labels = "") +
        labs(x = "Environment",
             y = "Trait Value",
             fill = "Species Abundance",
             subtitle = simul_label) +
        guides(colour = guide_legend(override.aes = list(size = 1, color = "grey50"))) +
        theme(legend.position = "top")
}
```

This document presents the relationships between functional traits of species and an environmental gradient.

Our coexistence model is developed following this equation:

$$N_{t+1, i, x} = \frac{R_{i, x} \times N_{t, i, x}}{1 + A \times \alpha}$$

with

$$\alpha_i = \sum_{j = 1, j \neq i}^{S} N_{t, j, x} \times (1 - \delta_{ij})$$

$$R_{i, x} = k \times \exp(- \frac{(trait_i - env_x)^2}{2\times {width}^2})$$

# Constant environmental filtering strength

@@

```{r no_compet_no_cor_abund_env, eval = FALSE}
plot_no_compet_no_cor_abund_env = fig_abund_env(no_compet_no_cor_df,
                                                no_compet_no_cor_label)

@@

```{r no_compet_no_cor_cwm_env, eval = FALSE}
plot_no_compet_no_cor_cwm_env = fig_cwm_env(no_compet_no_cor_df,
                                            no_compet_no_cor_label)
plot_no_compet_no_cor_cwm_env
```

```{r no_compet_no_cor_cwm_env_abund, eval = FALSE}
plot_no_compet_no_cor_cwm_env_abund = fig_cwm_env_abund(no_compet_no_cor_df,
                                                        no_compet_no_cor_label,
                                                        given_trans = "log10")

@@

@@

@@

@@

@@

@@

# With varying environmental filtering strength

In this section, the environmental filtering selects for a narrower trait range
towards the end of the environmental gradient.

```{r simul_no_compet_no_corr var_strength}

no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_no_cor_df_ind_landscape var_strength}
plot_no_compet_no_cor_df_ind_landscape = fig_ind_landscape(no_compet_no_cor_df,
                                                           no_compet_no_cor_label,
                                                           n_bins = 22,
                                                           given_trans = "identity")

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_low_cor_df_ind_landscape var_strength}
plot_no_compet_low_cor_df_ind_landscape = fig_ind_landscape(no_compet_low_cor_df,
                                                            no_compet_low_cor_label,
                                                            n_bins = 17,
                                                            given_trans = "identity")

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

```{r no_compet_high_cor_df_ind_landscape var_strength}
plot_no_compet_high_cor_df_ind_landscape = fig_ind_landscape(no_compet_high_cor_df,
                                                             no_compet_high_cor_label,
                                                             n_bins = 17)

```{r simul_compet_no_corr var_strength}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_no_cor_df_ind_landscape var_strength}
plot_compet_no_cor_df_ind_landscape = fig_ind_landscape(compet_no_cor_df,
                                                        compet_no_cor_label,
                                                        n_bins = 22)

```{r simul_compet_low_corr var_strength}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_low_cor_df_ind_landscape var_strength}
plot_compet_low_cor_df_ind_landscape = fig_ind_landscape(compet_low_cor_df,
                                                         compet_low_cor_label,
                                                         n_bins = 17)

```{r simul_compet_high_corr var_strength}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

```{r compet_high_cor_df_ind_landscape var_strength}
plot_compet_high_cor_df_ind_landscape = fig_ind_landscape(compet_high_cor_df,
                                                          compet_high_cor_label,
                                                          n_bins = 17)
plot_compet_high_cor_df_ind_landscape
```
